R for Clinical Study Reports and Submission

### 2021-08-26 tlf-overview.Rmd
tlf-overview.Rmd edited online with Bitbucket

A typical CSR contain full details of an individual clinical study 
including clinical and statistical description, presentations, and analyses. 
A large number of tables and figures are incorporated into the main text and appendices 
of a CSR. In CDISC pilot project, an [example CSR](file:///C:/Users/zhanyilo/OneDrive%20-%20Merck%20Sharp%20&%20Dohme,%20Corp/Desktop/cdiscpilot01.pdf) (??? This link is not workable)
is also provided. If you are interested in more examples of clinical study reports, 
the European Medicines Agency (EMA) publishes clinical data including 
clinical study reports submitted by pharmaceutical companies 
on [EMA clincal data website](https://clinicaldata.ema.europa.eu/web/cdp/home).

>>>>

A typical CSR contain full details of an individual clinical study 
including clinical and statistical description, presentations, and analyses. 
A large number of tables and figures are incorporated into the main text and appendices 
of a CSR. In CDISC pilot project, an [example CSR](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse/updated-pilot-submission-package/900172/m5/53-clin-stud-rep/535-rep-effic-safety-stud/5351-stud-rep-contr/cdiscpilot01/cdiscpilot01.pdf) 
is also provided. If you are interested in more examples of clinical study reports, 
the European Medicines Agency (EMA) publishes clinical data including 
clinical study reports submitted by pharmaceutical companies 
on [EMA clincal data website](https://clinicaldata.ema.europa.eu/web/cdp/home).
